---
title: "Sorting Algorithms Experiment Data Analysis"
author: "Mino Karadzhov,Kestutis Dikinis"
date: "12/8/2021"
output: html_document
---

Importing the required libraries + including a penalty for the scientific numbers.
```{r}
library(tidyverse)
options(scipen = 999)
```


```{r}
performanceData <- read.csv("../ExperimentResults/analysisReport.csv")
extendedPerformanceData <- read.csv("../ExperimentResults/base2Results.csv")
```


##Visualising the Results of our Experiments on a GGPlot
NB: This visualisation uses the growth with base 3.
### Using base 2 growth of Collections.
####Using geom_point + color aesthetic
```{r}
performanceData %>%
  ggplot(mapping = aes(x= CollectionSize, y = TimeComplexity, color = Sorter)) +
  geom_point() + geom_smooth()
```
#### Separated visualisation on efficent sorters (HeapSort and QuickSort)
```{r}
extendedPerformanceData %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>%
  ggplot(mapping = aes(x=CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() + geom_smooth()
```
#### Separated Visualisation on the slow sorters(SelectionSort, BogoSort)
```{r}
performanceData %>%
  filter(Sorter == "SelectionSort" | Sorter == "BubbleSort") %>%
  ggplot(mapping = aes(x = CollectionSize, y = TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth()
```

### Using base 2 for ColectionSize growth.
#### Using geom_point + geom_smooth and color aesthetic.
```{r}
extendedPerformanceData %>%
  ggplot(mapping = aes(x=CollectionSize, y = TimeComplexity, color = Sorter)) +
  geom_point() + geom_smooth()
```
####Separated view of the efficent sorters(HeapSort + QuickSort) 
```{r}
extendedPerformanceData %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>%
  ggplot(mapping = aes(x=CollectionSize, y = TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth()
```
```{r}
extendedPerformanceData %>%
  filter(Sorter == "BubbleSort" | Sorter == "SelectionSort") %>%
  ggplot(mapping = aes(x = CollectionSize, y = TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth()
```


1. Split the Heap And Quick + Bubble and Select
2. Try barChart.
3. hardware monitoring.
4. Structure the Research question better.
  NB: Include "Why is Time Complexity important" 
  5 We might want to change the TimeComplexity unit from nano to milisecond.
  

