---
title: "ExtendedExperimentDataAnalysis"
author: "Mino Karadzhov, Kestutis Dikinis"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
options(scipen=999)
experimentData <- read.csv("../ExperimentResults/extendedResults.csv")
```

```{r}
summary(experimentData)
```
#How does Memory usage and Time Complexity change as the collection grows 
```{r}
experimentData %>%
  ggplot(mapping = aes(x= TimeComplexity, y = RAMUsed)) +
  geom_point() +
  geom_smooth(method = "lm")
```



##How does Memory usage grow, as the collectionSize grows?
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y = RAMUsed)) +
  geom_point() + 
  geom_smooth(method = lm)
```
##How does Time grow, as the collectionSize grows?
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity)) +
  geom_point() +
  geom_smooth(method = lm)
```
### Comparing the different types of arrays in the context.
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = CollectionType)) +
  geom_point() +
  geom_smooth(method = lm)
```
### Comparing time required by different Sorting Algorithms per each CollectionType
#### Integer type arrays
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```
##### Closer look on the two separate group of sorters
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  filter(Sorter == "BubbleSort" | Sorter == "SelectionSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```

#### Char type arrays
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```
##### Closer look on the two separate group of sorters
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  filter(Sorter == "BubbleSort" | Sorter == "SelectionSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```

### Comparing memory used by different Sorting Algorithm per collectionType
#### int-type arrays
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  ggplot(mapping = aes(x= CollectionSize, y= RAMUsed, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```
#### char-type arrays
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  ggplot(mapping = aes(x= CollectionSize, y= RAMUsed, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```

#is RAM changing if we are executing separately ?
```{r}
separatedRuns <- read.csv("../ExperimentResults/separatedRuns.csv")
view(separatedRuns)
```
```{r}
separatedRuns %>%
  ggplot(mapping = aes(x= CollectionSize, y= RAMUsed, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```


