---
title: "ExtendedExperimentDataAnalysis"
author: "Mino Karadzhov, Kestutis Dikinis"
date: "2/2/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
options(scipen=999)
experimentData <- read.csv("../ExperimentResults/extendedResults.csv")
```

```{r}
summary(experimentData)
```
#How does Memory usage and Time Complexity change as the collection grows 
```{r}
experimentData %>%
  ggplot(mapping = aes(x= TimeComplexity, y = RAMUsed)) +
  geom_point() +
  ggtitle("")
```



##How does Memory usage grow, as the collectionSize grows?
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y = RAMUsed)) +
  geom_point() + 
  geom_smooth(method = "lm") +
  ggtitle("Changes in RAMUsed, as the size of collection grows")
```
##How does Time grow, as the collectionSize grows?
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Changes in TimeComplexity, as the size of collection grows")
```
### Comparing the different types of arrays in the context.
```{r}
experimentData %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = CollectionType)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Changes in TimeComplexity, when sorting different type of collections.")
```

### Comparing time required by different Sorting Algorithms per each CollectionType
#### Integer type arrays
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting an Integer collections, by using multiple different algorithms.")
```
##### Closer look on the two separate group of sorters
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting an Integer collections, by using the more efficient algorithms.")
```
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  filter(Sorter == "BubbleSort" | Sorter == "SelectionSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting an integer collections by using the less-efficient algorithms.")
```

#### Char type arrays
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting a charecter collections, by using multiple different Algorithms.")
```
##### Closer look on the two separate group of sorters
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  filter(Sorter == "QuickSort" | Sorter == "HeapSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting a charecter collections, by using the more efficient algorithms.")
```
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  filter(Sorter == "BubbleSort" | Sorter == "SelectionSort") %>% 
  ggplot(mapping = aes(x= CollectionSize, y= TimeComplexity, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) + 
  ggtitle("Sorting a charecter collections, by using the less-efficient algorithms.")
```

### Comparing memory used by different Sorting Algorithm per collectionType
#### Comparing the different types of collections 
```{r}
experimentData %>%
  ggplot(mapping = aes(x=CollectionSize, y = RAMUsed, color = CollectionType)) +
  geom_point() +
  geom_smooth() +
  ggtitle("Changes of memory usage, when sorting collections of different type.")
```

#### int-type arrays
```{r}
experimentData %>%
  filter(CollectionType == "int") %>%
  ggplot(mapping = aes(x= CollectionSize, y= RAMUsed, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm) +
  ggtitle("Sorting integer collections with multiple different sorting algorithms.")
```
#### char-type arrays
```{r}
experimentData %>%
  filter(CollectionType == "char") %>%
  ggplot(mapping = aes(x= CollectionSize, y= RAMUsed, color = Sorter)) +
  geom_point() +
  geom_smooth(method = lm)
```

